---
title: "COVID Alert App Analytics"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: bootstrap
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rsconnect)
library(rmarkdown)

library(dplyr)
library(tidyverse)
library(lubridate)
library(zoo)
library(reshape2)


library(data.table)

library(plotly)

Downloads <- fread("./datasets/Downloads.csv", encoding = 'UTF-8',data.table = F)
Uploads <- fread("./datasets/Uploads.csv", encoding = 'UTF-8',data.table = F)

Downloads$date <- as.Date(Downloads$date)
Downloads$cumulative_ios_downloads_canada <- as.integer(gsub(",","",Downloads$cumulative_ios_downloads_canada))
Downloads$cumulative_android_downloads_canada <- as.integer(gsub(",","",Downloads$cumulative_android_downloads_canada))
Downloads$cumulative_total_downloads_canada <- as.integer(gsub(",","",Downloads$cumulative_total_downloads_canada))
Downloads$daily_ios_downloads_canada <- as.integer(gsub(",","",Downloads$daily_ios_downloads_canada))
Downloads$daily_android_downloads_canada <- as.integer(gsub(",","",Downloads$daily_android_downloads_canada))
Downloads$daily_total_downloads_canada <- as.integer(gsub(",","",Downloads$daily_total_downloads_canada))

Uploads$date <- as.Date(Uploads$date)
```

Overview
===================================== 

Row {.tabset .tabset-fade}
-------------------------------------
    

 
### <b> Daily New Users </b> 
    
```{r}
#Daily OS Downloads 
osDL <- Downloads %>% 
  dplyr::select(date, daily_ios_downloads_canada, daily_android_downloads_canada, daily_total_downloads_canada) 
  
plot_ly(data = Downloads, 
        x = ~date, 
        y = ~daily_total_downloads_canada, 
        type = 'scatter', 
        mode = 'lines', 
        name = "Total Downloads", 
        
        hoverinfo = 'text',
        text = ~paste("+", format(daily_total_downloads_canada, big.mark =  ","), "<br>","New Users", sep = ""),
        
        showlegend = F, 
        line = list(color = "#F92672", width = 1.5)) %>% 
  
  add_trace(y = ~daily_ios_downloads_canada, name = "iOS", 
            line = list(color = "#007aff"), 
            hoverinfo = 'text',
            text = ~paste("+", format(daily_ios_downloads_canada, big.mark =  ","), "<br>","New iOS Users", sep = "")
            ) %>% 
  
  add_trace(y = ~daily_android_downloads_canada, name = "Android",
            line = list(color = "#4cd964"),
            hoverinfo = 'text',
            text = ~paste("+", format(daily_android_downloads_canada, big.mark =  ","), "<br>","New Android Users", sep = "")
            ) %>% 
  
  layout(xaxis = list(title = "", tickfont = list(color = "White")),
         yaxis = list(title = "User Growth", tickfont = list(color = "White")),
         hovermode = 'x unified', 
         plot_bgcolor  = "black",
         paper_bgcolor = "black")

``` 

### <b> Total Growth Rate </b> 
    
```{r}
Downloads <- Downloads %>% 
  dplyr::mutate(User_Growth = cumulative_total_downloads_canada - lag(cumulative_total_downloads_canada), 
                Growth_Rate = round(User_Growth / lag(cumulative_total_downloads_canada) * 100,2), 
                iOS_Growth = daily_ios_downloads_canada - lag(daily_ios_downloads_canada)
  )

plot_ly(data = Downloads, 
        x = ~date, 
        y = ~Growth_Rate, 
        type = 'scatter', 
        mode = 'lines', 
        
        #removing first value of 27K% user growth 
        
        transforms = list(list(type = 'filter',
                               target = 'y', 
                               operation = '<', 
                               value = 100)),
        line = list(color = "#F92672", width = 2), 
        
        hoverinfo = 'text',
        text = ~paste(format(Growth_Rate), "%", "<br>","User Growth", sep = "")) %>% 
  
  layout(xaxis = list(title = "", tickfont = list(color = "White")),
         yaxis = list(title = "User Growth", tickfont = list(color = "White")),
         hovermode = 'x unified', 
         plot_bgcolor  = "black",
         paper_bgcolor = "black")
``` 

Row
-------------------------------------
    
### <b> OS Composition </b> 
    
```{r}

# OS compositions
OS_comp <- Downloads %>% 
  dplyr::filter(date == max(date)) %>% 
  dplyr::select(cumulative_ios_downloads_canada,
                cumulative_android_downloads_canada) %>% 
  #convert columns to rows 
  tidyr::pivot_longer(
    cols = starts_with("cumulative_"), 
    names_to = "OS", 
    values_to = "Downloads", 
    names_prefix = "cumulative_")


OS_comp$OS[OS_comp$OS == "ios_downloads_canada"] <- "iOS"
OS_comp$OS[OS_comp$OS == "android_downloads_canada"] <- "android"

colors = c(
  #ios 
  "#007aff",
  #android 
  "#4cd964")

  plot_ly(data = OS_comp, 
        labels = ~OS, 
        values = ~Downloads, 
        type = 'pie', 
        marker = list(colors = colors, 
                      line = list(color = '#FFFFFF', width = 10)),
        showlegend = F, 
        
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#FFFFFF'),
        hoverinfo = 'text',
        text = ~paste(OS, "<br>",
                      format(Downloads, big.mark = ","), "Downloads", sep = " ")
        ) 
    
```

### <b> Cumulatives </b> 

```{r}
plot_ly(data = Downloads, 
        x = ~date, 
        y = ~cumulative_total_downloads_canada, 
        type = 'scatter', mode = 'lines', fill = 'tozeroy', name = "", 
        
        hoverinfo = 'text',
        text = ~paste("<br>", date, 
                      "<br>","+", format(cumulative_total_downloads_canada, big.mark =  ","), 
                      "<br>","Total Installs", sep = ""),
        
        showlegend = F) %>% 
  
  add_trace(y = ~cumulative_android_downloads_canada, name = "",
            hoverinfo = 'text',
            text = ~paste("<br>" ,
                          "+", format(cumulative_android_downloads_canada, big.mark =  ","), 
                          "<br>","Android Installs", sep = "")) %>% 
  
  add_trace(y = ~cumulative_ios_downloads_canada, name = "", 
            hoverinfo = 'text',
            text = ~paste("+", format(cumulative_ios_downloads_canada, big.mark =  ","), "<br>","iOS Installs", sep = "")) %>% 
  
  layout(xaxis = list(title = "", tickfont = list(color = "White")),
         yaxis = list(title = "Total App Installs", tickfont = list(color = "White")),
         hovermode = 'x unified', 
         plot_bgcolor  = "black",
         paper_bgcolor = "black")
```

Ontario 
===================================== 

About this Site 
===================================== 

#### Last Update  

`r format(Sys.time(), "%d %B, %Y")`

<br>

#### Background
*"Nothing in life is to be feared, it is only to be understood. Now is the time to understand more, so that we may fear less" - Marie Curie*  

<br>

#### Code
Code and input data used to generate this web app are available on [Github](https://github.com/Erebus54/Ontario-Covid19-Tracker-Dashboard).

<br>

#### Sources 

**COVID Alert Impact Data**: [Open Data Ontaro](https://data.ontario.ca/dataset/06a61019-62c1-48d8-8d4d-2267ae0f1144) broke down into the following two datasets: 

* COVID 19 Alert Downloads - Canada 
* Uploads of COVID-19 diagnosis to COVID Alert

*Contains information licensed under the Open Government Licence – Ontario*

<br>

#### Author 

Patrick Schnurbusch 

<br>

#### Contact 

patrick.schnurbusch@gmail.com
